IIIDYT at IEST 2018: Implicit Emotion Classification With Deep Contextualized Word Representations

### 2018-08-27 paper/paper.tex
Add images for paper, small fixes

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{emnlp2018}
% \usepackage[showframe=true]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{times}
\usepackage{latexsym}
\usepackage{lipsum}
\usepackage{url}
\usepackage{multirow}
\usepackage{changepage}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage[hang,flushmargin]{footmisc} % remove indentation from footnotes
% \hypersetup{draft}

@@

\author{Jorge A. Balazs, Edison Marrese-Taylor \and Yutaka Matsuo \\
  Graduate School of Engineering\\
  The University of Tokyo\\
  {jorge, emarrese, matsuo@weblab.t.u-tokyo.ac.jp} \\
}

@@

Additionally, we tried using the concatenation of the max-pooled, average-pooled and last hidden states of the BiLSTM as the sentence representation, following \citet{howard2018universal}, but found out that this impacted performance negatively. We hypothesize this is due to tweets being too short for needing such a rich representation. Also, the size of the concatenated vector was $4096\times3=12,288$, which probably could not be properly exploited by the 512-dimensional fully-connected layer.

@@

    \caption{Number of tweets on the test set with and without emoji and
    hashtags. The number between parentheses is the proportion of tweets
    correctly classified.}

>>>>

\documentclass[11pt,a4paper]{article}
\pdfoutput=1
\usepackage[hyperref]{emnlp2018}
% \usepackage[showframe=true]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{times}
\usepackage{latexsym}
\usepackage{lipsum}
\usepackage{url}
\usepackage{multirow}
\usepackage{changepage}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage[hang,flushmargin]{footmisc} % remove indentation from footnotes
% \hypersetup{draft}

@@

\author{Jorge A. Balazs, Edison Marrese-Taylor \and Yutaka Matsuo \\
  Graduate School of Engineering\\
  The University of Tokyo\\
  \{jorge, emarrese, matsuo\}@weblab.t.u-tokyo.ac.jp \\
}

@@

Additionally, we tried using the concatenation of the max-pooled, average-pooled and last hidden states of the BiLSTM as the sentence representation, following \citet{howard2018universal}, but found out that this impacted performance negatively. We hypothesize this is due to tweets being too short for needing such a rich representation. Also, the size of the concatenated vector was $4096\times3=12,288$, which probably could not be properly exploited by the $512$-dimensional fully-connected layer.

@@

    \caption{Number of tweets on the test set with and without emoji and
    hashtags. The number between parentheses is the proportion of tweets
    classified correctly.}
